Contracts for Contracts

### 2022-11-17 paper.tex
misc

@@

@@

smart contracts use callback, need for higher-order contract,
  Solidty already has "require" and "assert", but it doesn't deal with function values (NEED DOUBLE CHECK)
  %https://docs.soliditylang.org/en/v0.8.17/control-structures.html?highlight=require#panic-via-assert-and-error-via-require

@@

@@

the core model of the language

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.8]{beramono}
\usepackage{amsmath}
\usepackage{color}
\usepackage{xcolor,colortbl}
\usepackage{url}
\usepackage{listings}
\usepackage{paralist}
%\usepackage[compact]{titlesec}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{flushend}
\usepackage{textcomp}
\usepackage{pdfpages}
\usepackage{cleveref}
\usepackage{xspace}
\definecolor{light-gray}{gray}{0.85}

\input{macros}

@@

\lstMakeShortInline[keywordstyle=,%
                    flexiblecolumns=false,%
                    %basewidth={0.56em, 0.52em},%
                    mathescape=false,%
                    basicstyle=\ttfamily]@

@@

%https://docs.soliditylang.org/en/v0.8.17/control-structures.html?highlight=require#panic-via-assert-and-error-via-require
smart contracts use callback, need for higher-order contract,

One of the most adopted smart contract language Solidity indeed provides
linguistic mechanisms such as @require@ and @assert@ to enforce first-order
properties, however they does not deal with function values.
\todo{need double check}

Static verification cannot completely address the issue here since
transaction developers are oblivious to the user-provided callback.

It is unfortunate or even surprising that smart contract languages have not
adopted full-blown software contracts, especially higher-order contracts.

\subsubsection*{Contributions} This paper makes the following contributions:
\begin{itemize}
  \item We propose to add higher-order contracts to smart contract languages to
    improve the safety and reliability. We use Solidity to demonstrate our
    proposal.
  \item We present the core language ``Contract Solidity'' with higher-order
    contracts, including its syntax, formal semantics, and soundness.
  \item We examine a number of real-world cases and show that our proposal
    is effective in improving safety and reliability.
  \item We implement our approach on top of the existing Solidity compiler and shows
    that its runtime overhead is marginal.
\end{itemize}

@@

\begin{lstlisting}
  def test(x: Int): Int = x + 1
\end{lstlisting}

@@

the core model of the language (TODO named?)
\todo{there must be some interesting points/trade-offs about the design}
